% !TeX spellcheck = nl_NL
\chapter[Abstract]{\makebox[\linewidth]{Abstract}}
\vspace{-2.5em}\makebox[\linewidth]{\resizebox{0.9\linewidth}{1pt}{$\bullet$}}\bigskip

This is where you put your abstract. Ideally, it has the following structure (derived from the writing guide by \href{https://www.principiae.be/pdfs/TM&Th-2.0-summary.pdf}{Jean-Luc Doumont}). As an example, I have suffixed each point by a summary of the paragraphs of my own thesis abstract.
\begin{itemize}
    \item \emph{Context}: What is happening in the outside world that drove you to finding a need? (E.g.: "NLP has been booming since the advent of transformers.")
    \item \emph{Need}: Why did something have to be done? ("NLP models use tokenisers to turn text into processing units as a first step. The effect of how we do this has not been studied sufficiently.")
    \item \emph{Task}: What had to be undertaken? ("BPE, the most popular tokeniser, has known issues, but nobody has gathered these or analysed them.")
    \item \emph{Object}: What, in short, did you do, as described in this document? ("In this thesis, I set up a historical framework for subword tokenisation, verify a plethora of problems with BPE, and suggest a new augmentation. The first goal is achieved by...")

    \item \emph{Findings}: What did you discover after doing it? ("The analysis shows several fundamental drawbacks of BPE, and my augmentation is superior.")
    \item \emph{Concusion}: What does this mean with regards to the need? ("Using one tokeniser over the other does fundamentally matter, and BPE is not the best one.")
    \item \emph{Perspective}: What does the future of research hold, knowing this? ("My augmentation shows that improvement is possible, which provides exciting new research opportunities.")
\end{itemize}

This was shortened by \href{https://thomaswinters.be/}{Thomas Winters} as:

\begin{itemize}
	\item \emph{Context}: Why now? What is the background?
	\item \emph{Need}: Why you? Why is this useful to the reader?
	\item \emph{Task}: Why us? What are we solving?
	\item \emph{Object}: Why this document? How are we going to solve this?

	\item \emph{Findings}: What did we find?
	\item \emph{Conclusions}: So what? What do these results imply?
	\item \emph{Perspective}: What now? What does the future look like?
\end{itemize}

It also helps to \textbf{bold} the absolutely essential keywords of the abstract (fewer than five words, let's say) to let the reader know at a glance what your thesis is about.


\makebox[\linewidth]{\resizebox{0.9\linewidth}{1pt}{$\bullet$}}\bigskip